### 2023-11-21 main.tex
'
Reversibility correct

@@

We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute

@@

We fix $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$ and we have 

>>>>

In the most general case we have reversibility if 
	\alpha_{k}^{x}\left(|\alpha^{y}|-\alpha_{k}^{y}\right)=\alpha_{k}^{y}\left(|\alpha^{x}|-\alpha_{k}^{x}\right)\qquad \forall x,y\in V,\quad \forall k\in \{1,\ldots,N\}
	|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}
this is the multi-species counterpart of $\alpha\delta=\beta\gamma$ of the SEP case (see Section 3.2 of \cite{carinci2013duality}) \\
Should we say that or can we restrict to the case where $\alpha_{a}^{x}=\alpha_{a}$... Maybe we put a remark.\\

@@

We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute

@@

We fix $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
